### 2016-04-01 manuscript.Rnw
mention 1923 Fund in acknowledgments

We would like to thank the organizers of the OpenTree of Life APIs hackathon
that was held at the University of Michigan, Ann Arbor, 15-19 September, 2014,
where the development of \texttt{rotl} was started. We would also like to thank
Scott Chamberlain (rOpenSci) for providing a thorough code review, Scott
Chamberlain and Ross Mounce for commenting on the pre-print version of this
manuscript, Shinichi Nakagawa and Alistair Senior for their help in developing
the package's meta-analysis vignette, and Rich FitzJohn (Associate Editor) and
an anonymous reviewer for comments on the manuscript. DJW was supported by NIH
Grant R01-GM101352. FM was supported by iDigBio, and therefore this material is
based upon work supported by the National Science Foundation’s Advancing
Digitization of Biodiversity Collections Program (Cooperative Agreement
EF-1115210).

>>>>

We would like to thank the organizers of the OpenTree of Life APIs hackathon
that was held at the University of Michigan, Ann Arbor, 15-19 September, 2014,
where the development of \texttt{rotl} was started. We would also like to thank
Scott Chamberlain (rOpenSci) for providing a thorough code review, Scott
Chamberlain and Ross Mounce for commenting on the pre-print version of this
manuscript, Shinichi Nakagawa and Alistair Senior for their help in developing
the package's meta-analysis vignette, and Rich FitzJohn (Associate Editor) and
an anonymous reviewer for comments on the manuscript. DJW was supported by NIH
Grant R01-GM101352. FM was supported by 1923 Fund and by iDigBio, and therefore
this material is based upon work supported by the National Science Foundation’s
Advancing Digitization of Biodiversity Collections Program (Cooperative
Agreement EF-1115210).
